New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2023-04-18 02_paper/02_study/02_fitbit paper/fitbit_paper.tex
gvhj

@@

Teachers' average heart rate during the entire course of the study was approximately 96.84 bpm with a standard deviation of 14.44 and a range from 56 to 139 bpm.

>>>>

\begin{table}[h]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:demographicstable}Demographic Information}

\tiny{

\begin{tabular}{llllllllll}
\toprule
N & \multicolumn{1}{c}{Gender female in percent} & \multicolumn{1}{c}{M Age in years} & \multicolumn{1}{c}{SD Age in years} & \multicolumn{1}{c}{Min Age in years} & \multicolumn{1}{c}{Max Age in years} & \multicolumn{1}{c}{M Teaching Experience in years} & \multicolumn{1}{c}{SD Teaching Experience in years} & \multicolumn{1}{c}{Min Teaching Experience in years} & \multicolumn{1}{c}{Max Teaching Experience in years}\\
\midrule
70 & 60.00 & 29.74 & 10.67 & 19.00 & 59.00 & 4.84 & 9.31 & 0.00 & 37.00\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

@@

Teachers' average heart rate during the entire course of the study was approximately 96.83 bpm with a standard deviation of 14.40 and a range from 56 to 139 bpm.
